Generation of TypeScript Declaration Files from JavaScript Code

### 2021-05-18 mplr-2021/programming21-reviews-answered.txt

> ----------------------- REVIEW 1 ---------------------
> SUBMISSION: 28
> TITLE: Generation of TypeScript Declaration Files from JavaScript Code
> AUTHORS: Fernando Cristiani and Peter Thiemann
> 
> ----------- Overall evaluation -----------
> SCORE: -1 (major revision)
> ----- TEXT:
> Automatically generating TypeScript type signatures is a worthwhile
> goal; a mechanical process for generating such declarations would be
> less tedious, less error-prone, and more scalable. Pursuing a run-time
> trace-based technique is also compelling, given the significant
> difficulties that dynamically typed languages pose for static
> analysis. The initial results of the tool are promising: 244
> TypeScript declarations were automatically generated from existing
> module definitions, and 70 of these could be compared and validated
> against manually written declarations.
> 
> However, I believe the paper falls short both in terms of technical
> formulation as well as evidence of practical utility.
> 
> With respect to technical approach, the paper says (p.3/4) that the
> use of examples and dynamic analysis, rather than static analysis, is
> a novelty of the proposed tool. But a similar approach has been
> pursued previously:
> 
> * Trace Typing: An Approach for Evaluating Retrofitted Type Systems (Andreasen et al. ECOOP 2016)
> 
> * Just-in-Time Static Type Checking for Dynamic Languages (Ren et al. PLDI 2016)
> 
> * Dynamic Inference of Static Types for Ruby (An et al. POPL 2011)
> 
> * JSTrace: Run-time Type-Discovery for JavaScript (Saftoiu et al. 2010, > http://cs.brown.edu/research/plt/dl/flowtyping/v1/saftoiu-typediscovery-thesis.pdf)
> 
> How do the proposed techniques compare? Among these, trace typing is
> particularly relevant: like the current paper, it uses Jalangi for
> instrumentation.

Added discussion to the related work section.

> Besides not discussing this related work, the descriptions in Sections
> 4.2 and the end of 4.3 are rather informal: What exactly is the subset
> of JavaScript/TypeScript that is supported? What is the instrumented
> evaluator computing? How are types --- which include unions and
> intersections (at least for function types) --- being computed from
> the run-time information? The lack of precise details makes it
> difficult to understand what the tool currently does, how plausible it
> might be to extend to support more of JavaScript/TypeScript in the
> future, and how it relates the related work described above.
> 
> With respect to the implemented tool, it is not clear how close it is
> to being useful in practice. Many TypeScript features, as described in
> Table 1 and in the Evaluation, are not yet supported. For the 244
> modules for which declarations could be generated (and for the 70
> which could be compared to existing manual declarations): How many
> lines of code are in the modules? How many definitions are exported?
> How many examples were provided? How many examples were added to the
> 10 modules that were marked solvable? And how do these characteristics
> compare to the remaining Definitely Typed modules not currently
> supported? Especially because of the questions about technical
> formulation and novelty, it seems important for the system to come
> with a more comprehensive practical evaluation.
> 
> Overall, there is a lot of potential for this work --- especially on
> the practical side, for building a useful system --- but I think the
> results are preliminary to publish in their current form.
> 
> 
> *** Additional Comments and Questions ***
> 
> Fig 1: Does the tool generate declarations like this one? (If so, where
> does the name l__opts come from?)

Added explanation and a little cleanup.

> p.6: I think the reliance on Jalangi, as a black box, should be
> described earlier, along with related work.

Done.

> Fig 2: I spent some time wondering how the module names in (b) and (f)
> were chosen (the former appears to be camel case version of the module
> name, and the latter follows the name in the example program). Some of
> this explanation comes later, but perhaps it's worth adding more
> explanation here as this seems to be the primary place in the paper
> where the different kind of templates are explained.

Said that for Globtoregexp.I__opts already!

> Fig 3: Why not depict the example extraction step --- which sometimes
> includes manual addition of examples --- here? And consider
> representing Jalangi's role in this architecture.

Fernando?

> Sec 4.2/4.3: As mentioned, I think a lot more detail is warranted
> about the instrumentation and the process for computing types from
> traces.
> 
> "Execution of Code Examples": Interesting to see how many examples
> were perhaps out-of-date or were not proper examples. Were there any
> interesting patterns worth discussing?
> 
> p.17: It's encouraging to see how the proposed tool can fix some
> errors found in manual type declarations!
> 
> "Literal types vs string": If considering asking developers to mark
> strings, instead why not ask them to directly use, e.g. the "Enums" or
> "Discriminated Unions" (https://www.typescriptlang.org/docs/handbook)?
> 
> "Any": Ditto above; why not ask developers to choose the any type?
> 
> "Further types": Inferring indexed types, dependent types, etc. from
> run-time traces would seem to require quite significant technical
> extensions to the approach described here.
> 
> TSInfer: Is it fundamental that TSInfer apparently generates
> signatures for helpers? Could there not be a simple syntactic analysis
> that identifies top-level definitions, to be include in a declaration
> file?
> 
> 
> *** Minor Comments and Typos ***
> 
> Fig 1: Maybe I'm missing it, but I don't see Footnote 6 anywhere.j
> 
> p.5: "globToRegexp" ==> "GlobToRegexp" twice
> 
> p.8: I'm not sure why "syntax highlighting is done correctly" is
> noteworthy here.
> 
> Fig 4: Is this referenced in the text?
> 
> p.15: "loose" ==> "lose"
> 
> 
> 
> ----------------------- REVIEW 2 ---------------------
> SUBMISSION: 28
> TITLE: Generation of TypeScript Declaration Files from JavaScript Code
> AUTHORS: Fernando Cristiani and Peter Thiemann
> 
> ----------- Overall evaluation -----------
> SCORE: -1 (major revision)
> ----- TEXT:
> # Summary
> 
> The paper describes the tool dts-generate and its necessary companions to generate TypeScript declaration files for > JavaScript packages.
> These JavaScript packages need to provide a repository with a dedicated README that includes documentation efforts in the > form of exemplary usages.
> Based on the run-time information gathered by running these example, `dts-generate` produces the final TypeScript > declaration file after an additional analysis step that determines the scope of the file at hand (module, module-class, > module-function).
> The tool was evaluated based on all NPM packages that fulfilled the documentation requirement sufficiently and > community-driven declaration files; these declaration files are compared against the generated ones using an additional > tooling machinery developed by the authors. 
> 
> # My two cents
> 
> The general idea of the paper as well as the benefit of this idea (as well as the engineering effort) is worthwhile.
> The writing, on the other hand, does not feel mature enough for an acceptance.
> Unfortunately, I have problems myself to pin the exact reasons for this feeling.
> Let me try.
> 
> For an "empirical perspective" the evaluation (or here: result) section does not has the necessary depth to convince the > reader with, nor does it contain empirical methods (that I'm also not an expert for) that would strengthen the choice of this > perspective.
> Instead the results include further explanations of the engineering efforts necessary for the evaluation (how code examples > were extracted), single example extracts from the generated and original declaration files.
> The section concludes with a rather small paragraph (6.3 Evaluation) that only states that 70 files could be tested and all > qualified for a positive result.
> One deficit of this shallow evaluation origins from the small number of final declaration files that qualified for the evaluation.
> See some of the major and minor comments for more direct questions/remarks relating to specific sentences tackling this > deficiency.
> 
> The preceding part of the paper follows this rather shallow evaluation.
> The description of the engineering effort is given in detail, but not in depth.
> I guess these shallow descriptions are sufficient for a paper with an empirical emphasis, but since the focus of the current > version of paper is not the empirical part, I was wondering if an engineering perspective would be more suitable.
> In its current form, the description of the engineering effort needs additional work to make the shift to such an perspective > (what's the output the run-time information provided by Jalangi that dts-generate makes use of?).
> 
> All in all, I think that the paper needs a major revision (and shift of focus) in order to classify as empirical perspective or > needs to change the perspective to an engineering paper with additional efforts needed to fulfil the reader's wish to get more > in-depth insight to the technical part of this work.
> 
> ## Major comments
> 
> p. 1: I have the feeling that the abstract was not prepared in accordance to the specifications of the journal including the > keywords context, inquiry, approach, knowledge, grounding and importance.
> It's not that I do not get an impression of the work presented by the paper, but it just feels like an "ordinary abstract" and > not one that explicitly tackles the key questions behing the keywords above.
> 
> p. 4: "We examined all 6029 entries in the DefinitelyTyped repository and found 244 sufficiently well documented NPM > packages," - it's a shame that the final portion of repositories that can be tested is less than 5% of the starting value.
> 
> p. 15: "In this step, we loose another 50% of modules! This loss is mainly explained because some developers do not wrap > their code in a block using the javascript or js tags. However, as we are still left with code examples for 2260 modules, we did > not further look into code extraction as this number was considered sufficient for evaluating the generation of declaration > files." - Given the low value for the final number of repositories, you should definitely reconsider adapting your extraction > mechanism to be more robust!
> 
> p. 17: "We were unable to generate a declaration file based on the module-class template. All modules corresponding to this > template exhibited at least one of the unimplemented TypeScript features." - I was wondering if could make sense to adapt > the tooling machinery to leave out only the definitions that consist of unimplemented features, instead of leaving out a > whole module if one of its definition.
> 
> p. 18: "The remaining 174 files contained at least one of the unimplemented TypeScript features so that they could not be > considered." - This sentence sounds like you indeed generate as much as possible and filter out only layer --- how does this > statement relate my previous concern?
> 
> ## Minor comments
> 
> p. 5: "The choice of the template depends on the structure of the underlying JavaScript library:..." - here the following > listing/itemize environment seems to be missing, at least, I think that a itemize would be the better layout to use here.
> 
> p. 14: "dts-compare does not contemplate differences in function return types, because interface inference of function > return types is not covered in the current version of dts-generate." - Why is it that the inference for return types is that > different from parameters? You infer the parameters through example code, by running example code, you get concrete return > values that you can analyse in the same fashion. Furthermore, Figure 4 (for example) shows a generated file with functions > with return types. What am I missing here?
> ## Typos
> 
> all over the paper: runtime vs run time vs run-time!
> 
> p. 1: "..., which is error prone and time consuming." - error-prone
> p. 2: "..., which is time consuming and error prone." - error-prone
> p. 8: "A TypeScript Declaration File" - declaration file (why title-case?)
> p. 8: "... so that test cases were difficult to reap from the NPM packages:..." - read
> p. 9: "The Runtime Information block in Figure 3" - run-time information (why title-case?)
> p. 9: "For example, Function f ... Property foo ... Parameter a ... - function ... property ... parameter (it seems weird to start > with upper-case letters for the itemization)
> p. 11: " and traverse the Abstract Syntax Tree of a TypeScript program" - abstract syntax tree
> p. 12: "DefinitelyTyped Repository" - repository (why title-case?)
> p. 12: "uses the TypeScript Compiler API" - TypeScript compiler API (why title-case?)
> p. 18: "Excerpt of JS implementation that throws an Error when in- put parameter is not a string" - error
> p. 19: "Properties of interface Result were ignored for readability" - result
> p. 22: "future incorporation of a Symbolic Execution Engine that refines the" - symbolic execution engine (why title-case?)
> 
> ## Others
> p. 1: "from the TypeScript IDE and thus to incorrect uses of" - and, thus,  to
> p. 2: "a scripting language and thus lacks features for maintaining" - and, thus, lacks
> p. 4: "The implementation and the results are available under the following repositories:" -
> ...following repositories.
> p. 6: "It infers the overall structure of the JavaScript library,..." - non-referential _it_, why not write "the block infers..."
> p. 9: "...meaningful examples, thus avoiding possible cold start problems." - examples, thus, avoiding
> 
> 
> 
> ----------------------- REVIEW 3 ---------------------
> SUBMISSION: 28
> TITLE: Generation of TypeScript Declaration Files from JavaScript Code
> AUTHORS: Fernando Cristiani and Peter Thiemann
> 
> ----------- Overall evaluation -----------
> SCORE: -1 (major revision)
> ----- TEXT:
> The paper presents a tool that automatically generates TypeScript definition files for JavaScript projects. The tool uses > dynamic analysis. It runs the code samples found in the README file in the project repository, records information about > method invocations and argument values and uses those to generate type definitions. The paper evaluates the tool by > comparing generated definitions with hand-written definitions from the DefinitelyTyped repository - this is done for libraries > which have code samples in README, i.e. about ~270 out of ~6000.
> 
> The paper presents a tool that is useful, although it has a fairly limited scope. The approach presented by the authors - to > run a code sample using a library and use runtime monitoring to deduce the structure of the library - is definitely a promising > one. The authors make a good first step towards building a practical tool. However, the current implementation of the tool is > quite basic in a number of ways. First, it relies on code samples in README, which is not exactly common (it will work only > for quite basic libraries). Second, it ignores many interesting types that a library could use - most prominently arrays, but > those are just one example.
> 
> I believe the work presented in the paper is still interesting and useful, but it would need to be much more complete to > justify writing an extensive report about it. Although the journal does not have a specific category of "Tool" papers, I imagine > that if the authors presented the work in a shorter paper and clearly acknowledged the limitations and contributions, then it > would be interesting enough for publication. (Following the idea that the length of the paper should be commensurable with > the contribution.) The current version spends a quite a lot of time discussing the high-level structure of the tool and some > practical details which I did not find particularly important.
> 
> DETAILED COMMENTS
> 
> * In the introduction, you say that manually writing definitions is error-prone, but your paper then uses manually written > definitions from DefinitelyTyped as ground truth. I find this a bit paradoxical - maybe you could instead say that this is a lot > of work and there are many libraries that are not covered by DefinitelyTyped?
> 
> * I have to admit that I was a bit confused by the idea of "templates" that is used in the paper. Do the templates determine > just how you structure the definition, or are they somehow limiting what kind of constructs can be used in a given file? I think > this would benefit from some clarification in the paper.
> 
> * There is very little detail in the paper about how you infer types from the sample values that are observed during the > runtime execution. I guess the mechanism here is quite basic, but it is still worth discussing. (You might be interested in the > related paper [1] which does this for more complex types, but also covers things like records with optional fields.)
> 
> * I think your evaluation is somewhat limited by the fact that the libraries that have a complete documentation in the > README are the ones with very simple API. It would be interesting to evaluate how your approach works on larger libraries > (even if that meant copying some examples into a readme manually).
> 
> * I think the phrasing that "more advanced types are overblown" is a bit unfortunate, especially if the tool does not support > some quite basic types like arrays.
> 
> * The paper should give a much more extensive overview of related work - for example, it should discuss what has been > done using static analyses, whether similar tools exist for other languages and there might also be other interesting related > approaches (perhaps some based on machine learning methods). The references in the submission are fairly minimal.
> 
> [1] T. Petricek, G. Guera, D. Syme. Types from data: making structured data first-class citizens in F#, PLDI 2016

### 2021-05-18 mplr-2021/main.tex
reviewer #1 - related work

%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.

@@

\lstdefinelanguage{TypeScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, undefined,const},
  keywordstyle=\color{black}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this, declare, constructor, namespace, interface},
  ndkeywordstyle=\color{black}\bfseries,
  identifierstyle=\color{darkgray},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{lightgray}\slshape,
  stringstyle=\color{darkgray}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}

@@

Despite the advantages, it is unrealistic to expect the world to
switch to TypeScript in a day. Therefore, 
existing JavaScript libraries can be used in a TypeScript project by
adding a declaration file that contains a description of the library's
API in terms of types. 
The DefinitelyTyped repository~\cite{definitely-typed-repository} has
been created as a community effort to collect declaration files for
popular JavaScript libraries. At the time of writing it contains
declaration files for more than 6000 libraries.

@@

The novelty of our tool is twofold:
\begin{enumerate}
\item
  %% without the heavy lifting of static analysis
  We do not rely on static analysis, which is hard to implement
  soundly and precisely and which is prone to maintenance problems
  when keeping up with JavaScript's frequent language updates.
\item
  We extract example code from the programmer's library
  documentation and rely on dynamic analysis to extract typed usage
  patterns for the library from the example runs.
\end{enumerate}
% The architecture supports the future incorporation of a Symbolic
% Execution Engine that expands the initial code base using the
% signatures in the declaration file. The iterative process of exploring
% new execution paths will refine the generated declaration file in each
% iteration.

@@

The implementation and the results are available in the following repositories:

\begin{itemize}
  \item \url{https://github.com/proglang/run-time-information-gathering/tree/v1.1.0}
  \item \url{https://github.com/proglang/ts-declaration-file-generator/tree/v1.5.0}
  \item \url{https://github.com/proglang/ts-declaration-file-generator-service/tree/v1.2}
  \item \url{https://github.com/proglang/dts-generate-method/tree/v1.3.1}
  \item \url{https://github.com/proglang/dts-generate-results/tree/v1.4.0}
\end{itemize}

@@

\section{Motivating Example}
\label{sec:motivating-example}
The \NPM{} package \texttt{glob-to-regexp} provides functionality to turn a
glob expression for matching filenames in the shell into a regular
expression\footnote{\url{https://www.npmjs.com/package/glob-to-regexp}}. It 
has about 9.9M weekly downloads and 188 \NPM{} packages depend on it. If
a developer creates or extends TypeScript code that depends on the
\texttt{glob-to-regexp} library, the TypeScript
compiler and IDE require a declaration file for that library to
perform static checking and code completion, respectively. With
\texttt{dts-generate} we automatically generate a TypeScript
declaration file for \texttt{glob-to-regexp}. Our tool downloads the \NPM{} 
package, runs the examples extracted from its documentation, gathers
run-time information, and generates a TypeScript declaration
file. The result is 
shown in \figref{fig:motivating-example-glob-to-regexp-vscode} and it is
ready for use in a TypeScript project. For example,  Visual Studio's
code completion runs properly with the generated file
(\figref{fig:motivating-example-glob-to-regexp-vscode}). If the
\texttt{glob-to-regexp} package gets modified in the future, a new declaration
file can be generated automatically using
\texttt{dts-generate}. Our comparator tool (Section~\ref{sec:dts-compare}) can compare the new file
for incompatibilities with the previous declaration file.

@@

The declaration file shown in \figref{fig:motivating-example-glob-to-regexp-vscode}
describes a package with a single exported function. The first parameter is of type
\texttt{string} and the second one is an optional object described by an interface. TypeScript namespaces
organize types declared in a declaration file and avoid name clashes with other types
\cite{typescript-namespaces}. For example, the interface
\lstinline[language=TypeScript]{I__opts} is declared in namespace
\lstinline[language=TypeScript]{globToRegexp} in
\figref{fig:motivating-example-glob-to-regexp-vscode}. Hence its uses
must be qualified by the namespace as in
\lstinline[language=TypeScript]{globToRegexp.I__opts}.

@@

The examples and the code base of the library are instrumented with
Jalangi \cite{DBLP:conf/sigsoft/SenKBG13} to gather data flow
information and type information at run time. Jalangi is a configurable
framework for dynamic analysis of JavaScript. It provides several
analysis modules that we extended as needed to retrieve the required
run-time information.
%, which is then saved in a JSON file.

@@

\section{Related Work}
\label{sec:related-work}
\paragraph*{dts-gen}
TypeScript comes with \texttt{dts-gen}, a tool that creates declaration files for
JavaScript libraries \cite{dts-gen}. Its documentation states that the result is 
intended to be used as a starting point for the development of a declaration file. The outcome
needs to be refined afterwards by the developer.

>>>>

%% MPLR Format: up to 12 pages, excluding bibliography and appendix)
%%
%% This is file `sample-sigconf.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%% The first command in your LaTeX source must be the \documentclass command.

@@

\lstdefinelanguage{TypeScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break, undefined,const},
  keywordstyle=\color{black}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this, declare, constructor, namespace, interface},
  ndkeywordstyle=\color{black}\bfseries,
  identifierstyle=\color{darkgray},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{lightgray}\slshape,
  stringstyle=\color{darkgray}\ttfamily,
  morestring=[b]',
  morestring=[b]"
}
%"

@@

Despite the advantages, it is unrealistic to expect the world to
switch to TypeScript in a day. Therefore, 
existing JavaScript libraries can be used in a TypeScript project by
adding a declaration file that describes the library's
API in terms of types. 
The DefinitelyTyped repository~\cite{definitely-typed-repository} has
been created as a community effort to collect declaration files for
popular JavaScript libraries. At the time of writing it contains
declaration files for more than 6000 libraries.

@@

The main contribution of our tool is twofold:
\begin{enumerate}
\item
  %% without the heavy lifting of static analysis
  We do not rely on static analysis, which is hard to implement
  soundly and precisely and which is prone to maintenance problems
  when keeping up with JavaScript's frequent language updates.
\item
  We extract example code from the programmer's library
  documentation and rely on dynamic analysis to extract typed usage
  patterns for the library from the example runs.
\end{enumerate}
% The architecture supports the future incorporation of a Symbolic
% Execution Engine that expands the initial code base using the
% signatures in the declaration file. The iterative process of exploring
% new execution paths will refine the generated declaration file in each
% iteration.

@@

Our implementation of code instrumentation  to gather data flow
information and type information at run time is based on
Jalangi \cite{DBLP:conf/sigsoft/SenKBG13}, a configurable
framework for dynamic analysis for JavaScript.
The implementation and the results are available in the following repositories:

\begin{itemize}\footnotesize
  \item \url{https://github.com/proglang/run-time-information-gathering/tree/v1.1.0}
  \item \url{https://github.com/proglang/ts-declaration-file-generator/tree/v1.5.0}
  \item \url{https://github.com/proglang/ts-declaration-file-generator-service/tree/v1.2}
  \item \url{https://github.com/proglang/dts-generate-method/tree/v1.3.1}
  \item \url{https://github.com/proglang/dts-generate-results/tree/v1.4.0}
\end{itemize}

@@

\section{Motivating Example}
\label{sec:motivating-example}
The \NPM{} package \texttt{glob-to-regexp} provides functionality to turn a
glob expression for matching filenames in the shell into a regular
expression\footnote{\url{https://www.npmjs.com/package/glob-to-regexp}}. It 
has about 9.9M weekly downloads and 188 \NPM{} packages depend on it. If
a developer creates or extends TypeScript code that depends on the
\texttt{glob-to-regexp} library, the TypeScript
compiler and IDE require a declaration file for that library to
perform static checking and code completion, respectively. With
\texttt{dts-generate} we automatically generate a TypeScript
declaration file for \texttt{glob-to-regexp}. Our tool downloads the \NPM{} 
package, runs the examples extracted from its documentation, gathers
run-time information, and generates a TypeScript declaration
file. The result is 
shown in \figref{fig:motivating-example-glob-to-regexp-vscode} and it is
ready for use in a TypeScript project:  Visual Studio's
code completion runs properly with the generated file. If the
\texttt{glob-to-regexp} package gets modified in the future, a new declaration
file can be generated automatically using
\texttt{dts-generate}. Our comparator tool (Section~\ref{sec:dts-compare}) can compare the new file
for incompatibilities with the previous declaration file.

@@

The generated declaration file shown in \figref{fig:motivating-example-glob-to-regexp-vscode}
describes a package with a single exported function. The module name
is derived from the NPM module name by camlization\footnote{i.e.,
  transforming to camel case.}. The first parameter is of type
\texttt{string} and the second one is an optional object described by
an interface. To avoid name clashes, \texttt{dts-generate} creates a
namespace that corresponds to the module name. This pattern is a best
practice to  organize types declared in a declaration file
\cite{typescript-namespaces}. In the example, the interface
\lstinline[language=TypeScript]{I__opts} is declared in namespace
\lstinline[language=TypeScript]{globToRegexp}. Hence, its uses
must be qualified by the namespace as in
\lstinline[language=TypeScript]{globToRegexp.I__opts}. The name of the
interface is derived from the name of the formal parameter.

@@

The examples and the code base of the library are instrumented with
Jalangi \cite{DBLP:conf/sigsoft/SenKBG13} to gather data flow
information and type information at run time. Jalangi provides several
analysis modules that we extended as needed to retrieve the required
run-time information.
%, which is then saved in a JSON file.

@@

\section{Related Work}
\label{sec:related-work}
\paragraph*{Dynamic analysis techniques} Trace Typing
\cite{DBLP:conf/ecoop/AndreasenGCSTS16} is a framework for evaluating
retrofitted type systems. It involves gathering traces of JavaScript program
executions, just like in our system. However, the goal of the type
systems that they study is quite different from ours. They are
interested in type information to improve run-time performance and
traditional compilation, giving information about object layout and
tag tests. Contrary to their approach, we do not just observe the
types of arguments and return values. In addition, we also trace
property accesses which translate to requirements on objects. Also, we
have no generalization step to infer polymorphic types.

Hummingbird \cite{DBLP:conf/pldi/RenF16} is a system for type checking
Ruby programs at run time in the presence of
metaprogramming. Metaprograms are extended to additionally generate
type annotations for the generated code. Once a generated method is
called, the method's body is statically checked against the actual
argument types as well as the generated annotations. This system does
not involve run-time tracing.

Rubydust \cite{DBLP:conf/popl/AnCFH11} implements dynamic
constraint-based type inference for Ruby. Rubydust runs an
instrumented Ruby program that gathers subtyping constraints for
parameters and return types of methods as well as for fields, which is
quite different from the interaction that we collect. After
completion, the solution of these constraints is proposed as a typing
for the program. These types are sound if the runs cover sufficiently
many paths in the program. Rubydust is reasonably effective because
Ruby's type system is nominal. For JavaScript, this approach is much
less effective as (run-time) typing is structural
\cite{DBLP:conf/sfp/NausT16}.

JSTrace \cite{saftoiu21:_jstrac} also performs dynamic type inference
for JavaScript by gathering information at run time. It inspects the
run-time types of arguments and return values of suitably wrapped
functions. While the resulting information is treated similarly as in
our work, we also gather interactions that result from property
accesses and method calls and derive further typing constraints from
those. Moreover, JSTrace performs an (expensive) deep inspection of
the types of objects and arrays whereas our inspection is shallow and
thus more efficient.

None of the works tackles the question how to obtain a sufficient
sample of run-time information. One part of our contribution is to
systematically uncover the README files as a driver for running the
JavaScript code under inspection.

\paragraph*{dts-gen}
TypeScript comes with \texttt{dts-gen}, a tool that creates declaration files for
JavaScript libraries \cite{dts-gen}. Its documentation states that the result is 
intended to be used as a starting point for the development of a declaration file. The outcome
needs to be refined afterwards by the developer.
